---
title: "RMarkdown Template"
author: "James Long"
always_allow_html: yes
bibliography: refs.bib
output:
  html_document:
    theme: united
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r alternative-preables,echo=FALSE,include=FALSE,eval=FALSE}
## add date
date: "05/20/2020"

## if using word replace output with
output:
  word_document:
    toc: yes

## if using pdf replace output with
output:
  pdf_document:
    toc: yes
header-includes:
  - \usepackage{xcolor}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## colorizes text when using html or pdf output
## just spits out text x for word
colorize <- function(x, color) {
  if(color=="todo"){
    color <- "red"
    x <- paste0("TODO: ",x)
  }
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}

todo <- function(x){
  paste0("**",colorize(x,"todo"),"**")
}
```

## Resources

Many ideas here are taken/adapted from [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/)

## Colored Text and Todos

These work for html/pdf. Print uncolored text in docx.

`r todo("do more work here")`

`r colorize("this is blue","blue")`


## Citations

I wrote an article about positive-unlabeled learning [@lin2020flexible]. @lin2020flexible connects positive unlabeled learning with multiple testing.

## Numbering Equations

## Bibliography
